Verifying Concurrent Search Structure Templates for C Programs using VST

### 2023-04-20 concurrency/CONCUR 2023/paper.tex
fix breakage

\section{Proof Mechanization}
We describe the mechanized formal verification of the correctness of such these templates, implemented in C and verified with the VST, using concurrent separation logic (CSL) to reason about the behavior of the C code, and integrated Iris-style logical atomicity into VST. All proofs are formalized in Coq using VST, and can be found online at

>>>>

\section{Proof Mechanization}
We present the mechanized formal verification of the correctness of these templates, which are implemented in C and verified with the Verified Software Toolchain (VST). We employ concurrent separation logic (CSL) to analyze the behavior of the C code and incorporate Iris-style logical atomicity within VST.

By utilizing VST, we can create programs in standard C, automatically generate abstract syntax trees (ASTs) for them in Coq, and subsequently state and interactively prove specifications for these programs with the support of automated tactics. All proofs are formalized in Coq using VST and can be found online at
